%-------------------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec} 
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
 
    
    
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5.7pt}}

%-------------------------------------------

\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Humberto A. Raniolo Infante} \\ \vspace{1pt}
    \small (+1) 763-238-6552 $|$ \href{mailto:humberto.raniolo@gmail.com}{\underline{humberto.raniolo@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/humberto-raniolo-b1a116190/}{\underline{linkedin.com/in/humberto-raniolo-sa4/}} $|$
    \href{https://github.com/wololo-aeyoyo}{\underline{github.com/wololo-aeyoyo}}
\end{center}

%-----------Objective-----------
\section*{Objective}
Currently focused on building stable, scalable, and reliable solutions using best practices and design patterns on cloud or on-premise environments, with the goal of improving performance and maintainability.

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
\renewcommand{\baselinestretch}{0.5} 

    \resumeSubheading
      {Reliability Engineer – Observability}{September 2023 – Present}
      {BestBuy}{Richfield, MN}
      \begin{itemize}
      \setlength\itemsep{-0.1em}
      \item Built and managed a complex IT monitoring and observability services leveraging Splunk, Elastic, Graphite, Grafana, and VictoriaMetrics for on-prem and cloud-based delivery.
      \item Contributed to the successful migration of the Splunk Enterprise cluster to the Splunk Cloud solution.
      \item Developed an automated process for generating new indexes within the Splunk Cloud environment.
      \item Experience and leverage Terraform, ruby, ansible to implement AWS Services.
      \item Implemented multiple Chef cookbooks to automate application deployment, ensuring consistency, manageability, and idempotency.
      \item Leverage and deployed open-source tooling for network monitoring.
      \end{itemize}

      
    \resumeSubheading
      {Software Developer – Web Development}{February 2023 - May 2023}
      {Accentio Studios}{Remote}
      \begin{itemize}
      \setlength\itemsep{-0.1em}
      \item Developed a system to manage challenges for the 500 historias app using microservices architecture with NodeJS and NestJs and implemented RabbitMQ as a message broker for asynchronous communication.
      \item Utilized Docker to containerize services, ensuring isolation, scalability, and efficient deployment.
      \end{itemize}

      \resumeSubheading
      {Software Engineer – Web Development}{2021 – 2023}
      {Credicard Consortium}{Caracas, Venezuela}
      \begin{itemize}
      \setlength\itemsep{-0.1em}
      \item Wrote backend software for web services REST APIs in Node.js using the NestJS framework, SQL databases (MariaDB, PostgreSQL) and Springboot-Java to connect to legacy IBM-DB2 banking data.
      \item Leveraged OpenLdap to build user login authentication services that were successfully scaled to handle thousands of concurrent users.
      \item Configured CI/CD workflows for a suite of android apps leveraging the Flutter SDK.
      \item Engineered a scalable payment processing system for prepaid credit cards utilizing tools such as Angular, Node.JS and Springboot.
      \end{itemize}

    \resumeSubheading
      {Software Developer – Intern}{2019-2020}
      {Telefónica Venezolana C.A}{Caracas, Venezuela}
      \begin{itemize}
      \setlength\itemsep{-0.1em}
      \item Optimized software systems used for billing conciliation and interconnections utilizing tools such as C\#, Java Struts 2 and SQL Server.
      \end{itemize}
    \resumeItemListEnd

%-----------PROJECTS-----------
\section{Projects}

    \resumeSubHeadingListStart
         
      \resumeProjectHeading
          {\textbf{[ASM, C++] Data conversion for pressure measurement to sent} $|$ \emph{Pic16f887, Arduino}}{April 2018}
          \resumeItemListStart
            \resumeItem{Designed and built a circuit using an Esp8266 and a PIC16F887 to collect data from a tension transducer measuring tensile stress, sending the data to a Google Sheets document and an Android application for visualization.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {UNEXPO - Luis caballero Mejias University}{Caracas, Venezuela}
      {Bachelor of Science Systems Engineering}{August 2020}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Node.Js, Ruby, Python, Java, C\#, JavaScript, HTML, CSS.} \\
     \textbf{Frameworks}{: Angular, NestJS, SpringBoot. } \\
     \textbf{Technologies}{: AWS, Terraform, Chef, Ansible. }  \\
     \textbf{Certifications:}{ \href{https://www.credly.com/badges/43b10234-742d-44fc-8052-a21e5bfabc13/linked_in_profile}{Splunk Cloud Administration}, 
     \href{https://www.credly.com/badges/782d7907-5cf9-49ac-93d0-72e30cc4947e/linked_in_profile}{Splunk Cluster Administration} , and 
     \href{https://www.credly.com/badges/39ba9c1d-1279-4a77-a183-28c1bcb6ec7a/linked_in_profile}{Using the Splunk REST API.}} }}
 \end{itemize}


%-------------------------------------------
\end{document}
